How to compute the fusion product of MV cycles in type A

### 2021-02-22 draft.tex
about nondom mu_i
so long as sum is dom
typo in coweight as point of GL(K) descr

Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\mu_1} \\
    & (t-s)^{\mu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\mu_m}
\end{bmatrix} 
\]
which we will view in $\GL_m(R) $ for any ring $ R $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ R = \Ks, \CC(t)$).

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.

>>>>

Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\mu_1} \\
    & (t-s)^{\mu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\mu_m}
\end{bmatrix} 
\]
which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. \acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions? or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}
